### 2009-04-06 talk/icooolps2009-dotnet/clibackend.tex
display block ids in bold instead of red, else color-blind reviewers complain :-)

The picture in Figure~\ref{block-id-fig} shows a graph composed of three methods (for
simplicity, dispatchers are not shown); method ids are in red, whereas
block numbers are in black. 
The graph contains three external links; in particular, note the link
between blocks \texttt{0x00020001} and \texttt{0x00010001} which
connects two blocks implemented by different methods.
\begin{figure}[h]
\begin{center}
\includegraphics[height=6cm]{blockid}
\caption{Method and block ids.}\label{block-id-fig}
\end{center}
\end{figure}

>>>>

The picture in Figure~\ref{block-id-fig} shows a graph composed of three methods (for
simplicity, dispatchers are not shown); method ids are in bold, whereas
block numbers are in black. 
The graph contains three external links; in particular, note the link
between blocks \texttt{0x00020001} and \texttt{0x00010001} which
connects two blocks implemented by different methods.
\begin{figure}[h]
\begin{center}
\includegraphics[height=6cm]{blockid}
\caption{Method and block ids.}\label{block-id-fig}
\end{center}
\end{figure}
